%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------    

\cventry
{Developer} % Job title
{CICPC. System for police investigation and information (SIIPOL)} % Organization
{Caracas, Venezuela} % Location
{Feb. 2009 - Apr. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Java}
\item {JSF}
\item {Spring Framework}
\item {Hibernate}
\item {Acegi Security System}
\item {Rich Faces}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Project Leader and developer} % Job title
{National database of vaccination of Venezuela} % Organization
{Caracas, Venezuela. 2011} % Location
{Jun. 2011 - Oct. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {C#, SQLServer, Solr}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Architect/Developer} % Job title
{ZERA. FISIM. Mathematical Physical Simulator)} % Organization
{La Havana, Cuba} % Location
{2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Java / Java Web Start / PostgreSQL / PHP / REST / SSO}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Architect / Analyst / Developer} % Job title
{Physical simulation platform Computational Mathematics Center} % Organization
{Santiago de Cuba, Cuba} % Location
{2014-2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {C++ / Java / Charm++ / OpenMP / MPI / CUDA}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Architect / Analyst / Developer} % Job title
{Integration of banking applications for Qatar Islamic Bank (QIB)} % Organization
{Santiago de Cuba, Cuba} % Location
{2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {C++ / Java / Charm++ / OpenMP / MPI / CUDA}
\item {Processing and analysis Big Data}
\item {Oracle}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer} % Job title
{Procedures and Services of the Tax Administration Service (SAT) of Mexico} % Organization
{Santiago de Cuba, Cuba} % Location
{2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Java / Oracle WebCenter Sites / Oracle DB}
%\item {}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Team Leader} % Job title
{Document loans management system (MGAF)} % Organization
{Comlombia} % Location
{2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Java / JPA / AngularJS / Oracle / PostreSQL / Spring Security / Junit}
%\item {}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Team Leader} % Job title
{Police Management System (PMS) of Barcelona, Spain} % Organization
{Barcelona, Spain} % Location
{2015-2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Java / JPA / AngularJS / Oracle / PostreSQL / Spring Security / Junit / JHipster / Yeoman}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

