%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Positions}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------   

\cventry
{Cuba Team Leader} % Job title
{BlueOcean Tech} % Organization
{La Havana, Cuba} % Location
{Dec. 2016 - current} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Team Leader for AI, Java, PHP teams}
\end{cvitems}
}

%------------------------------------------------      

\cventry
{Team Leader for Qatar Islamic Bank Database project} % Job title
{SOAINT, Cuba division} % Organization
{La Havana, Cuba} % Location
{Sep. 2014 - Sep. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Processing and analysis Big Data}
\item {Oracle}
\item {IBM Integration toolkit / PLSQL / SOAUI / Webphere MQ}
\end{cvitems}
}


%------------------------------------------------   

\cventry
{Computer Simulation Team Leader} % Job title
{Center of Computational Mathematics} % Organization
{La Havana, Cuba} % Location
{Sep. 2014 - Feb. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Research/implementation about Parallel Evolutionary Algorithms.}
\item {Computational fluid simulation of biological interest}
\item {HPC}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Editor in Chief of the Cuban Computer Science Magazine} % Job title
{University of Informatics Sciences} % Organization
{La Havana, Cuba} % Location
{Jun. 2014 - Oct. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Editor in Chief}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Researcher} % Job title
{Research Management Department at the University of Informatics Sciences} % Organization
{Havana, Cuba} % Location
{Sep. 2011 - Jun. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Establish the scientific policy of research groups.}
\item {Coordination of international projects}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Internship} % Job title
{Jülich Supercomputing Centre (JSC)} % Organization
{Jülich, Germany} % Location
{Aug. 2015, Aug. 2016 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Computational fluid simulation}
\item {Applying parallel and distributed computing both high performance CPU and GPU}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Chief of the National Vaccine Database} % Job title
{Government from Venezuela} % Organization
{Caracas, Venezuela} % Location
{Aug. 2010, Aug. 2011 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Team leader}
\item {Distributed database system}
\item {Data analysis}
\item {Database replication}
\item {Real time response researcher}
\item {C#, SQLServer, Solr}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Developer of the Police Management System} % Job title
{Government from Venezuela} % Organization
{Caracas, Venezuela} % Location
{Aug. 2010, Aug. 2011 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {System analyst}
\item {Java Developer}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

